Countries by Region
========================================================

Json files of countries by region have been downloaded to 
/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/Region/

```{r}
url <- 'http://api.worldbank.org/countries?region=SAS&format=json'
savedFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/regionSAS.json"
download.file(url, destfile = savedFile, method = "curl")
```
which includes the following files

regionEAP.json  East Asia and Pacific (developing only)
regionEAS.json  East Asian and Pacific
regionECA.json  Europe and Central Asia
regionLAC.json  Latin America and Carribean
regionMEA.json  Middle East and North Africa
regionNAC.json  North America
regionSAS.json  South Asia
regionSSF.json  Sub-Saharan Africa

To load the table of countries from a particular region, for example East Asia and Pacific, use the following code.
```{r}
savedFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/Region/regionEAS.json"
library(jsonlite)
jsonData <- fromJSON(savedFile)
regionEAS <- jsonData[[2]]; # result is a list of length 2 of which we want the second element
regionEAS <- flatten(regionEAS); # removes nesting of data tables
regionEAS <- tbl_df(regionEAS); # dplyr more user friendly
View(regionEAS)

```

To then count the number of countries in each income level use:
```{r}
regionEAS %>% count(incomeLevel.id)
```

Repeating over all regions.
```{r}
savedFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/Region/regionECA.json"
jsonData <- fromJSON(savedFile)
regionECA <- jsonData[[2]]; # result is a list of length 2 of which we want the second element
regionECA <- flatten(regionECA); # removes nesting of data tables
regionECA <- tbl_df(regionECA); # dplyr more user friendly
regionECA %>% count(incomeLevel.value)
```

```{r}
savedFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/Region/regionLAC.json"
jsonData <- fromJSON(savedFile)
regionECA <- jsonData[[2]] %>% flatten() %>% tbl_df()
regionECA %>% count(incomeLevel.value)
```

```{r}
savedFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/Region/regionMEA.json"
jsonData <- fromJSON(savedFile)
region <- jsonData[[2]] %>% flatten() %>% tbl_df()
region %>% count(incomeLevel.value)
```

```{r}
savedFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/Region/regionNAC.json"
jsonData <- fromJSON(savedFile)
region <- jsonData[[2]] %>% flatten() %>% tbl_df()
region %>% count(incomeLevel.value)
```

```{r}
savedFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/Region/regionSAS.json"
jsonData <- fromJSON(savedFile)
region <- jsonData[[2]] %>% flatten() %>% tbl_df()
region %>% count(incomeLevel.value)
```

```{r}
savedFile <- "/Users/jamesmungall/MyR/GettingCleaningData/data/worldBank/Region/regionSSF.json"
jsonData <- fromJSON(savedFile)
region <- jsonData[[2]] %>% flatten() %>% tbl_df()
region %>% count(incomeLevel.value)
```

