Week1 quiz              10.6.15
========================================================

##Question 1.
============

Dowload file
```{r}
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv 
?accessType=DOWNLOAD"
download.file(fileUrl, destfile = "./data/housing.csv", method = "curl")
```

Then download the code book, https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf 

We want to find the number of properties with a value >= $1000,000. According to the code book, this corresponds to properties with a VAL of 24.

```{r}
df <- read.csv('data/housing.csv', stringsAsFactors=F)
result = df %>% count(VAL)
View(result)
```
This allows me to see that there are 53 properties with this VAL.

## Question 3
--------------
Download the Excel spreadsheet on Natural Gas Aquisition Program here: 

```{r}
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx?accessType=DOWNLOAD"
download.file(fileUrl,destfile="./data/naturalGas.xlsx",method="curl")
dateDownloaded <- date()
```

Read rows 18-23 and columns 7-15 into R and assign the result to a variable called dat

```{r}
library(xlsx)
colIndex <- 7:15
rowIndex <- 18:23
dat <- read.xlsx("./data/naturalGas.xlsx",sheetIndex=1,header=TRUE, colIndex=colIndex,rowIndex=rowIndex)
```

(original data source: http://catalog.data.gov/dataset/natural-gas-acquisition-program)

## Question 4
-------------
 Read the XML data on Baltimore restaurants from here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml 

How many restaurants have zipcode 21231?

```{r}

library(XML)
library(RCurl)
fileURL <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"
xData <- getURL(fileURL)
doc <- xmlParse(xData)
rootNode <- xmlRoot(doc)
xmlName(rootNode)

allZipcodes <- xpathSApply(rootNode,"//zipcode",xmlValue)

zipDf  = data_frame(allZipcodes)
result =zipDf %>% count(allZipcodes)
View(result)
```
We can see that the number of restaurants with zipcode 21231 is 127 restaurants.

## Question 5
The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv 

using the fread() command load the data into an R object
 DT 
Which of the following is the fastest way to calculate the average value of the variable
pwgtp15 
broken down by sex using the data.table package?

n.b. file has already been downloaded from question 1.

```{r}
DT <- fread('data/housing.csv', stringsAsFactors=F)

system.time(mean(DT[DT$SEX==1,]$pwgtp15))
system.time(sapply(split(DT$pwgtp15,DT$SEX),mean))
system.time(DT[,mean(pwgtp15),by=SEX])
system.time(tapply(DT$pwgtp15,DT$SEX,mean))
```
